Test parsing of Proff.no table

### 2022-07-07 Test parsing of Proff table.Rmd
Update title.

---
title: "Test parsing of Proff.no table (Kreftforeningen)"
author: "Torbjørn Skinnemoen Ottersen"
date: '2022-07-06'
output: 
  html_document: 
    df_print: paged
---

>>>>

---
title: "Test parsing of Proff.no table"
author: "Torbjørn Skinnemoen Ottersen"
date: '2022-07-06'
output: 
  html_document: 
    df_print: paged
---
